Verifying Demonstrations

### 2018-02-26 paper/intro.tex
change to intro

Consider the following scenario in which Alice is an activist that organizes a protest against the current regime leader Eve in some location(s).
On one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Eve is an autocrat who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Eve.
However, they might also be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Eve's regime. 
To verify how many participated in Alice's protest, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.

After many demonstrations the count by police and that by the organizers 
differ, for legitimate\footnote{%
  A difference is actually quite natural, as the counts have different goals.
  The organizers want to count everyone who ever participated.
  Police want to estimate the count at the peak of participation, due to crowd 
  control~\cite{2016DemonstrationsInSeoul}.
} or other reasons, in some instances the difference can be hundreds of thousands.
There are numerous examples where there is difficulty in establishing the actual 
number of participants, e.g.:\@ the demonstrations against the president in 
South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration 
attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March 
in the US~\cite{2017WomensMarchesInUS}, the demonstrations against changing the 
constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the 
independence of Catalonia~\cite{CataloniaDemonstrations}.
The methods for counting the crowds vary.
Most of the available methods lack precision, i.e.\ they have large error 
margins.
They can only give an estimate for a particular snapshot in time, e.g.\ at the 
peak of the event, not the cumulative participation count --- at least not 
without counting some people multiple times, which in turn increases the error 
of the estimation.
Finally, they also lack verifiability, i.e.\ everyone must trust the entity who
does the counting.
(We will discuss them in more detail in \cref{RelatedWork}.)

We can make one important observation about this problem that has not
been adequately addressed in the design of existing crowd-counting solutions: it is an adversarial setting.
Alice the activist has an incentive to increase the tallied number of 
participants, whereas Eve (and possibly other interests) have an incentive to 
decrease the tallied number of participants.
In this case we have two options:
either we trust Alice or Eve, or we must verify their claims.
Our main goal is to provide a scheme which prevents both Alice and Eve from 
cheating, i.e.\ we aim for verifiable claims.
To solve this problem, we need a verifiable participation count which is 
protected from Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest.

\subsection{Combining properties of electronic voting with location proofs}

\subsection{Contributions}

We propose a protocol which provides a way for protests to be securely verified.
Additionally, this verification system does not incur any additional risk to 
protesters' privacy than participating in the physical protest itself.

@@

\subsection{Roadmap}
The rest of the paper is organized as follows. First, we define the
system model for verifiable privacy-preserving crowd counting.  We then
present the desired security properties for such a system and subsequently discuss related
work in terms of these properties. We give the relevant background on
the building blocks of our solution and then describe our proposal for
distance-bounding anonymous credentials that copes with a malicious
(impersonating) verifier. We then present the protocol constructed
from the building blocks, its security and privacy analysis, and
finally our conclusions.

>>>>

\emph{Context.} Consider the following illustrative scenario in which Alice is an activist that organizes a protest against the current regime leader Eve in some location(s).
On one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Eve is an autocrat who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Eve.
However, they might also be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Eve's regime. 
To realize this objective a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.

Historically, there are many examples of protests in which the count estimated by police and that by the organizers 
differ significantly, sometimes in the order of hundreds of thousands.
The difference is actually quite natural as both parties have different objectives.
More precisely, the organizers want to count everyone who have participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
Among the numerous recent examples in which it is difficult to establish the actual number of participants, we can cite the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.

Existing methods for crowd-counting varies significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
However, most of them lack precision (\emph{i.e.}, they have large error margins) and they can only give an estimate for a particular snapshot in time (\emph{e.g.}, at the peak of the event). 
In particular, the existing methods cannot estimate reliably the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they also lack verifiability as everyone has to trust the entity responsible for performing the counting.
Finally, one important observation about crowd-counting that has been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting.

Indeed, going back to our example Alice the activist has an incentive to increase the tallied number of participants, whereas Eve (and possibly other entities) have an incentive to decrease the tallied number of participants.
In this case, we are left with two options: either we trust Alice or Eve or we have to be able to verify their claims.
In this paper, our main objective is to provide a scheme preventing both Alice and Eve from cheating (\emph{i.e.}, their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist to Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent a physical eavesdropper from recognizing a particular individual in a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated to his identity and that his actions are also unlinkable.

%Seb: I suggest that we give a name to the protocol to be able to refer to it more adequately
\emph{Contributions} We propose a scheme that provides a way for protests to be securely verified.
Additionally, this verification system does not incur any additional risk to 
protesters' privacy than participating in the physical protest itself.

@@

\emph{Outline.} The paper is organized as follows. 
First, we define the system model for verifiable privacy-preserving crowd counting.  We then
present the desired security properties for such a system and subsequently discuss related
work in terms of these properties. We give the relevant background on
the building blocks of our solution and then describe our proposal for
distance-bounding anonymous credentials that copes with a malicious
(impersonating) verifier. We then present the protocol constructed
from the building blocks, its security and privacy analysis, and
finally our conclusions.

%Seb: I suggest that we move this part to system model
\subsection{Combining properties of electronic voting with location proofs}
